QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-11-04 Revision/Paper_Rev.tex
Rev_V8.4

\begin{abstract}
In the realm of mobile edge computing (MEC), efficient computation task offloading plays a pivotal role in ensuring a seamless quality of experience (QoE) for users. Maintaining a high QoE is paramount in today's interconnected world, where users demand reliable services. This challenge stands as one of the most primary key factors contributing to handling dynamic and uncertain mobile environment. In this study, we delve into computation offloading in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We formulate the computation task offloading problem as a Markov decision process (MDP) to maximize the long-term QoE of each user individually. We propose a distributed QoE-oriented computation offloading (QECO) algorithm based on deep reinforcement learning (DRL) that empowers mobile devices to make their offloading decisions without requiring knowledge of decisions made by other devices. Through numerical studies, we evaluate the performance of QECO. \textcolor{red}{
	Simulation results reveal that compared to the state-of-the-art existing works, QECO increases the number of completed tasks by up to 14.4\%, while simultaneously reducing task delay and energy consumption by 9.2\% and 6.3\%, respectively. Together, these improvements align with user preferences, resulting in a significant average QoE enhancement of 37.1\%. This substantial improvement is achieved by accurately accounting for user dynamics and edge server workloads while making intelligent offloading decisions. This highlights QECO's effectiveness in enhancing MEC systems.}

@@

%\textcolor{red}{Consequently, it can complete 14\% more tasks and reduce task delay and energy consumption by 10.7\% and 11.7\%, respectively. These together contribute to a significant improvement of at least 37\% in average QoE compared to an existing algorithm.}
\end{abstract}

@@

Efficient task offloading in MEC is a complex optimization challenge due to the dynamic nature of the network and the variety of MDs and servers involved \cite{jiang2019toward} \cite{TNSE-WU-24}. In particular, determining the optimal offloading strategy, scheduling the tasks, and selecting the most suitable EN for task offloading are the main challenges that demand careful consideration. \textcolor{red}{In addition to the dynamic network changes, the uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges that can significantly impact the MEC systems.}

@@

To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives. \textcolor{red}{However, the traditional RL methods are not efficient to  handle  environments with high-dimensional state  spaces. Deep reinforcement learning (DRL) combines  traditional RL  with  deep  neural  networks  to  intelligently respond to the unknown and dynamic system when addressing the limitations of RL-based algorithms. Despite these advancements, task offloading still faces significant challenges in real-world scenarios with multiple MDs and ENs. In such scenarios, it is essential for MDs to make offloading decisions independently  without prior knowledge of other MDs’ tasks and offloading models. However,  existing works fail to adequately address this challenge. In addition, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly estimate the QoE value and address the user demands and requirements. Although deep Q-networks (DQN) offer a valuable tool, a more comprehensive approach is required to accurately estimate the QoE while addressing the aforementioned challenges in practical scenarios where global information is limited.}

In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance.   \textcolor{red}{We propose a distributed QoE-oriented computation offloading (QECO) algorithm to efficiently handle task offloading in uncertain loads at ENs.} This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. 
  \textcolor{red}{To capture the dynamic nature of the MEC environment, we employ the dueling double deep Q-network (D3QN), which is a refined improvement over standard DQN model. By integrating both double Q-learning \cite{van2016deep} and dueling network architectures \cite{wang2016dueling}, D3QN reduces overestimation bias in action-value predictions and more accurately distinguishes the relative importance of states and actions. We also incorporate long short-term memory (LSTM) \cite{hochreiter1997long} into our D3QN model to continuously estimate dynamic workloads at ENs. This enables MDs to effectively handle the uncertainty of the MEC environment, where global information is limited, and proactively adjust the offloading strategies to improve their long-term QoE estimation.} By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

@@

\begin{itemize}
	\item \textit{Task Offloading Problem in the MEC System:} \textcolor{red}{ We consider queuing systems for MDs and ENs and formulate the task offloading problem as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). We aim to maximize the long-term QoE, which reflects the task completion rate, task delay, and energy consumption of MDs. Our problem formulation effectively utilizes the resources and properly handles the dynamic fluctuations of workload at ENs. }
	%We formulate the task offloading problem in queuing-based MEC as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). Given task completion, task delay, and energy consumption as the QoE requirements of MDs, this approach concentrates on maximizing the long-term QoE, by effectively utilizing the resources and properly handling the dynamic nature of workload at ENs.

@@

	\item \textit{Performance Evaluation:} \textcolor{red}{We conduct comprehensive experiments to evaluate QECO’s performance and training convergence against baseline schemes as well as two state-of-the-art existing works. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs while taking the dynamic workloads at ENs into consideration. In particular, it converges more quickly than vanilla DQN and DDQN methods. QECO also improves average QoE by 37.1\% and 29.8\% compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed} and distributed and collective DRL-based offloading algorithm (DCDRL)~\cite{qiu2020distributed}, respectively.}

@@

\end{itemize}
The structure of this paper is as follows.  \textcolor{red}{Section~\ref{section:II} reviews the related works.} Section~\ref{section:III} presents the system model, followed by the problem formulation in Section ~\ref{section:IV}. In Section~\ref{section:V}, we present the algorithm, while Section~\ref{section:VI} provides an evaluation of its performance. Finally, we conclude in Section~\ref{section:VII}. \color{blue}
\section{Related Work}
\label{section:II}
%\textcolor{black}{We explore state-of-the-art techniques characteristic to discuss how they address task offloading problems in scenarios that need to process massive data with limited devices in MEC, such as the Internet of Things (IoT), Internet of Vehicles (IoV), and Industrial IoT (IIoT)  environment. 
%Internet of Things (IoT) \cite{dai2020edge}, \cite{liao2023online}, \cite{Bolourian-WCL24}, 
%Internet of Vehicles (IoV) \cite{Bolourian-WCL24}, 
%and Industrial IoT (IIoT)  environment \cite{gong2022edge}, \cite{wu2023multi}, \cite{wu2024combining}
%, while uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges in MEC systems with limited resources. 
% \textcolor{blue}{In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment. We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table1} provides an intuitive comparison of the related works.}
  In recent years, numerous studies have focused on computation offloading in MEC, covering a broad range of applications, including IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive}. 
%To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment. 
To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of DRL in adapting to environmental changes and learning optimal strategies. In this section, we explore the current DRL-based state-of-the-art works and discuss their strengths and limitations. Table~\ref{table1} provides an intuitive comparison of these works.
\subsection{DRL-based Optimization Methods for MEC}

@@

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{red}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes,~\cite{wang2020intelligent},~\cite{zhang2019toward},~\cite{allahham2022multi}. We consider $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.
%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.

@@

We model the edge execution by the queues associated with MDs deployed at ENs. \textcolor{purple}{If computation task $z_i(t')$ is dispatched to EN $j$ in time $t' < t$, we let $z_{i,j}^{\text{E}}(t)$, $\lambda_{i,j}^{\text{E}}(t)$ (in bits), and $\rho_{i,j}^{\text{E}}(t)$ denote the unique index of the task, the task size, and the number of CPU cycles required per unit of the task in the $i^{\text{th}}$ queue at EN $j$, respectively. } We define $\eta_{i,j}^{\text{E}}(t)$ (in bits) as the length of this queue at the end of time slot $t \in \mathcal{T}$. We refer to a queue as an active queue in a certain time slot if it is not empty. That being said, if at least one task is already in the queue from previous time slots or there is a task arriving at the queue, that queue is active. We define $\mathcal{B}_j(t)$ to denote the set of active queues at EN $j$ in time slot $t$.

@@

Additionally, we define $D_{i,j}^{\text{E}}(t)$ to represent the quantity of processing time slots allocated to task $z_{i,j}^{\text{E}}(t)$ when executed at EN $j$. This value is given by:
%\begin{alignat}{1}
%	D_{i,j}^{\text{E}}(t) =  {\,\, \lambda_{i,j}^{\text{E}}(t) \rho_i(t) \,\,\, \over f_j^{\text{E}} \tau /  b_j(t)}.
%	\label{14}  
%\end{alignat}
\begin{alignat}{1}
		\textcolor{purple}{D_{i,j}^{\text{E}}(t) =  l_{i,j}^{\text{E}}(t)-\hat{l}_{i,j}^{\text{E}}(t).}
	\label{14}  
\end{alignat}

We also define $E_{i,j}^{\text{E}}(t)$ as the energy consumption of processing at EN $j$ in time slot $t$ by MD $i$. This can be calculated as:
%\begin{alignat}{1}
%	E_{i,j}^{\text{E}}(t) =  { D_{i,j}^{\text{E}}(t)  p_j^{\text{E}} \tau \,\, \over b_j(t)},  % = { \lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over  f_j^{\text{E}}}p_j^{\text{E}} ,
%%	\label{15}  
%\end{alignat}
\begin{alignat}{1}
	\textcolor{purple}{E_{i,j}^{\text{E}}(t) =  \sum_{t^{'}=\hat{l}_{i,j}^{\text{E}}(t)}^{l_{i,j}^{\text{E}}(t)}\hspace{-2mm}{\, p_j^{\text{E}} \tau \over \,\, b_j(t^{'})\,\,}\mathbbm{1}(i \in \mathcal{B}_j(t^{'})),}  
	\label{15}  
\end{alignat}
where $p_j^{\text{E}}$ is a constant value which denotes the energy consumption of the EN $j$'s processor when operating at full capacity.

In addition to the energy consumed by EN $j$ for task processing, we also take into account the energy consumed by the MD $i$'s user interface in the standby state while waiting for task completion at the EN $j$. We define $E_{i}^{\text{I}}(t)$ as the energy consumption associated with the user interface of MD $i \in \mathcal{I}$, which is given by
%\begin{alignat}{1}
%	E_{i}^{\text{I}}(t) =  \textcolor{blue}{\sum_{\mathcal{J}}y_{i,j}(t)} D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
%	\label{16}
%\end{alignat}
\begin{alignat}{1}
		\textcolor{purple}{E_{i}^{\text{I}}(t) =  \sum_{j \in \mathcal{J}}y_{i,j}(t) D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, }
	\label{16}
\end{alignat}
where $p_i^{\text{I}}$ is the standby energy consumption of MD $i \in \mathcal{I}$.  \textcolor{blue}{Recall that $y_{i,j}(t)$ is the offloading indicate function. Moreover, among all $j \in \mathcal{J}$, $y_{i,j}=1$ only for one $j$ which is the corresponding EN.}

%\textcolor{red}{We also denote the total energy consumption for the offloaded task $z_{i,j}^{\text{E}}(t)$ in time slot $t$ as $E^{\text{O}}_i(t)$, which is,}
%\begin{alignat}{1}
%	\textcolor{blue}{E_i^{\text{O}}(t) = E_i^{\text{T}}(t) +  \textcolor{blue}{\sum_{\mathcal{J}}y_{i,j}(t) \,} E_{i,j}^{\text{E}}(t) + E_i^{\text{I}}(t)}.
%	\label{17}
%\end{alignat}

@@

\subsection{State Space}
A state in our MDP represents a conceptual space that comprehensively describes the state of an MD facing the environment. We represent the MD $i$'s state in time slot $t$ as vector $\boldsymbol{s}_i(t)$ that includes the newly arrived task size, the queues information, the MD's \textcolor{blue}{energy level of the battery}, and the workload history at the ENs. The MD observers this vector at the beginning of each time slot. The vector $\boldsymbol{s}_i(t)$ is defined as follows:
\begin{alignat}{1}
\boldsymbol{s}_i(t) = \Big(\lambda_i(t), \delta_i^{\text{C}}(t), \delta_i^{\text{T}}(t), \boldsymbol{\eta}_i^{\text{E}}\hspace{-0.4mm}(\hspace{-0.4mm}t\hspace{-0.4mm}-\hspace{-0.4mm}1\hspace{-0.5mm}),\phi_i(t), \mathcal{H}(t) \Big),
	\label{18}
\end{alignat}
where vector $\boldsymbol{\eta}_i^{\text{E}}(t-1) = (\eta_{i,j}^{\text{E}}(t-1))_{j \in \mathcal{J}}$ represents the queues length of MD $i$ in ENs at the previous time slot and is computed by the MD according to \eqref{10}. 
\textcolor{red}{Since MDs are assumed to be battery-operated, their operation modes are aligned with those of real-world devices. Let $\phi_i(t)$ represent the \textcolor{blue}{battery level percentage of MD $i$} at time slot $t$, where $\phi_i(t)$ is selected from the discrete set $\Phi = \{\phi_1, \phi_2, \phi_3\}$, corresponding to ultra power-saving, power-saving, and performance modes, respectively.}

@@

\subsection{QoE Function}
\textcolor{red}{The QoE function reflects user satisfaction with task computation, whether using local or edge resources. QoE accounts for task completion rate, processing delay, and energy consumption. Each user may have unique QoE requirements~\cite{wang2017qoe}. Therefore, we define a multi-dimensional, adaptive structure to assess QoE, balancing these factors according to the MDs preferences, such as prioritizing reduced task delays or energy savings, which may vary over time~\cite{wang2019intelligent},~\cite{mehrabi2019energy}. To capture personalized QoE requirements, we define QoE as a weighted sum of the above factors. Each MD dynamically adjusts these weights to reflect the importance of different factors based on its energy modes, which are performance, power-saving, and ultra-power-saving modes. We now calculate task delay and energy consumption and then introduce the associated cost and QoE function.}

@@

\textcolor{purple}{$\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+x_i(t) \bigg( E_i^{\text{T}}(t) + $
\begin{alignat}{1}
	\hspace{1.2cm}    E_i^{\text{I}}(t) +  \sum\limits_{j \in \mathcal{J}}  \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big)
	  E_{i,j}^{\text{E}}(t')\bigg).
	\label{22}  
\end{alignat}}

>>>>

\begin{abstract}
In the realm of mobile edge computing (MEC), efficient computation task offloading plays a pivotal role in ensuring a seamless quality of experience (QoE) for users. Maintaining a high QoE is paramount in today's interconnected world, where users demand reliable services. This challenge stands as one of the most primary key factors contributing to handling dynamic and uncertain mobile environment. In this study, we delve into computation offloading in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We formulate the computation task offloading problem as a Markov decision process (MDP) to maximize the long-term QoE of each user individually. We propose a distributed QoE-oriented computation offloading (QECO) algorithm based on deep reinforcement learning (DRL) that empowers mobile devices to make their offloading decisions without requiring knowledge of decisions made by other devices. Through numerical studies, we evaluate the performance of QECO. \textcolor{blue}{
	Simulation results reveal that compared to the state-of-the-art existing works, QECO increases the number of completed tasks by up to 14.4\%, while simultaneously reducing task delay and energy consumption by 9.2\% and 6.3\%, respectively. Together, these improvements align with user preferences, resulting in a significant average QoE enhancement of 37.1\%. This substantial improvement is achieved by accurately accounting for user dynamics and edge server workloads while making intelligent offloading decisions. This highlights QECO's effectiveness in enhancing MEC systems.}

@@

%\textcolor{blue}{Consequently, it can complete 14\% more tasks and reduce task delay and energy consumption by 10.7\% and 11.7\%, respectively. These together contribute to a significant improvement of at least 37\% in average QoE compared to an existing algorithm.}
\end{abstract}

@@

Efficient task offloading in MEC is a complex optimization challenge due to the dynamic nature of the network and the variety of MDs and servers involved \cite{jiang2019toward} \cite{TNSE-WU-24}. In particular, determining the optimal offloading strategy, scheduling the tasks, and selecting the most suitable EN for task offloading are the main challenges that demand careful consideration. \textcolor{blue}{In addition to the dynamic network changes, the uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges that can significantly impact the MEC systems.}

@@

To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives. \textcolor{blue}{However, the traditional RL methods are not efficient to  handle  environments with high-dimensional state  spaces. Deep reinforcement learning (DRL) combines  traditional RL  with  deep  neural  networks  to  intelligently respond to the unknown and dynamic system when addressing the limitations of RL-based algorithms. Despite these advancements, task offloading still faces significant challenges in real-world scenarios with multiple MDs and ENs. In such scenarios, it is essential for MDs to make offloading decisions independently  without prior knowledge of other MDs’ tasks and offloading models. However,  existing works fail to adequately address this challenge. In addition, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly estimate the QoE value and address the user demands and requirements. Although deep Q-networks (DQN) offer a valuable tool, a more comprehensive approach is required to accurately estimate the QoE while addressing the aforementioned challenges in practical scenarios where global information is limited.}

In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance.   \textcolor{blue}{We propose a distributed QoE-oriented computation offloading (QECO) algorithm to efficiently handle task offloading in uncertain loads at ENs.} This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. 
  \textcolor{blue}{To capture the dynamic nature of the MEC environment, we employ the dueling double deep Q-network (D3QN), which is a refined improvement over standard DQN model. By integrating both double Q-learning \cite{van2016deep} and dueling network architectures \cite{wang2016dueling}, D3QN reduces overestimation bias in action-value predictions and more accurately distinguishes the relative importance of states and actions. We also incorporate long short-term memory (LSTM) \cite{hochreiter1997long} into our D3QN model to continuously estimate dynamic workloads at ENs. This enables MDs to effectively handle the uncertainty of the MEC environment, where global information is limited, and proactively adjust the offloading strategies to improve their long-term QoE estimation.} By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

@@

\begin{itemize}
	\item \textit{Task Offloading Problem in the MEC System:} \textcolor{blue}{ We consider queuing systems for MDs and ENs and formulate the task offloading problem as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). We aim to maximize the long-term QoE, which reflects the task completion rate, task delay, and energy consumption of MDs. Our problem formulation effectively utilizes the resources and properly handles the dynamic fluctuations of workload at ENs. }
	%We formulate the task offloading problem in queuing-based MEC as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). Given task completion, task delay, and energy consumption as the QoE requirements of MDs, this approach concentrates on maximizing the long-term QoE, by effectively utilizing the resources and properly handling the dynamic nature of workload at ENs.

@@

	\item \textit{Performance Evaluation:} \textcolor{blue}{We conduct comprehensive experiments to evaluate QECO’s performance and training convergence against baseline schemes as well as two state-of-the-art existing works. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs while taking the dynamic workloads at ENs into consideration. In particular, it converges more quickly than vanilla DQN and DDQN methods. QECO also improves average QoE by 37.1\% and 29.8\% compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed} and distributed and collective DRL-based offloading algorithm (DCDRL)~\cite{qiu2020distributed}, respectively.}

@@

\end{itemize}
The structure of this paper is as follows.  \textcolor{blue}{Section~\ref{section:II} reviews the related works.} Section~\ref{section:III} presents the system model, followed by the problem formulation in Section ~\ref{section:IV}. In Section~\ref{section:V}, we present the algorithm, while Section~\ref{section:VI} provides an evaluation of its performance. Finally, we conclude in Section~\ref{section:VII}. \color{blue}
\section{Related Work}
\label{section:II}
%\textcolor{black}{We explore state-of-the-art techniques characteristic to discuss how they address task offloading problems in scenarios that need to process massive data with limited devices in MEC, such as the Internet of Things (IoT), Internet of Vehicles (IoV), and Industrial IoT (IIoT)  environment. 
%Internet of Things (IoT) \cite{dai2020edge}, \cite{liao2023online}, \cite{Bolourian-WCL24}, 
%Internet of Vehicles (IoV) \cite{Bolourian-WCL24}, 
%and Industrial IoT (IIoT)  environment \cite{gong2022edge}, \cite{wu2023multi}, \cite{wu2024combining}
%, while uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges in MEC systems with limited resources. 
% \textcolor{blue}{In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment. We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table1} provides an intuitive comparison of the related works.}
  In recent years, numerous studies have focused on computation offloading in MEC, covering a broad range of applications, including IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive}. 
%To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment. 
To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of DRL in adapting to environmental changes and learning optimal strategies. In this section, we explore the current DRL-based state-of-the-art works and discuss their strengths and limitations. Table~\ref{table1} provides an intuitive comparison of these works.
\subsection{DRL-based Optimization Methods for MEC}

@@

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{blue}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes,~\cite{wang2020intelligent},~\cite{zhang2019toward},~\cite{allahham2022multi}. We consider $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.
%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.

@@

We model the edge execution by the queues associated with MDs deployed at ENs. \textcolor{blue}{If computation task $z_i(t')$ is dispatched to EN $j$ in time $t' < t$, we let $z_{i,j}^{\text{E}}(t)$, $\lambda_{i,j}^{\text{E}}(t)$ (in bits), and $\rho_{i,j}^{\text{E}}(t)$ denote the unique index of the task, the task size, and the number of CPU cycles required per unit of the task in the $i^{\text{th}}$ queue at EN $j$, respectively. } We define $\eta_{i,j}^{\text{E}}(t)$ (in bits) as the length of this queue at the end of time slot $t \in \mathcal{T}$. We refer to a queue as an active queue in a certain time slot if it is not empty. That being said, if at least one task is already in the queue from previous time slots or there is a task arriving at the queue, that queue is active. We define $\mathcal{B}_j(t)$ to denote the set of active queues at EN $j$ in time slot $t$.

@@

Additionally, we define $D_{i,j}^{\text{E}}(t)$ to represent the quantity of processing time slots allocated to task $z_{i,j}^{\text{E}}(t)$ when executed at EN $j$. This value is given by:
%\begin{alignat}{1}
%	D_{i,j}^{\text{E}}(t) =  {\,\, \lambda_{i,j}^{\text{E}}(t) \rho_i(t) \,\,\, \over f_j^{\text{E}} \tau /  b_j(t)}.
%	\label{14}  
%\end{alignat}
\begin{alignat}{1}
		\textcolor{blue}{D_{i,j}^{\text{E}}(t) =  l_{i,j}^{\text{E}}(t)-\hat{l}_{i,j}^{\text{E}}(t).}
	\label{14}  
\end{alignat}

We also define $E_{i,j}^{\text{E}}(t)$ as the energy consumption of processing at EN $j$ in time slot $t$ by MD $i$. This can be calculated as:
%\begin{alignat}{1}
%	E_{i,j}^{\text{E}}(t) =  { D_{i,j}^{\text{E}}(t)  p_j^{\text{E}} \tau \,\, \over b_j(t)},  % = { \lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over  f_j^{\text{E}}}p_j^{\text{E}} ,
%%	\label{15}  
%\end{alignat}
\begin{alignat}{1}
	\textcolor{blue}{E_{i,j}^{\text{E}}(t) =  \sum_{t^{'}=\hat{l}_{i,j}^{\text{E}}(t)}^{l_{i,j}^{\text{E}}(t)}\hspace{-2mm}{\, p_j^{\text{E}} \tau \over \,\, b_j(t^{'})\,\,}\mathbbm{1}(i \in \mathcal{B}_j(t^{'})),}  
	\label{15}  
\end{alignat}
where $p_j^{\text{E}}$ is a constant value which denotes the energy consumption of the EN $j$'s processor when operating at full capacity.

In addition to the energy consumed by EN $j$ for task processing, we also take into account the energy consumed by the MD $i$'s user interface in the standby state while waiting for task completion at the EN $j$. We define $E_{i}^{\text{I}}(t)$ as the energy consumption associated with the user interface of MD $i \in \mathcal{I}$, which is given by
%\begin{alignat}{1}
%	E_{i}^{\text{I}}(t) =  \textcolor{blue}{\sum_{\mathcal{J}}y_{i,j}(t)} D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
%	\label{16}
%\end{alignat}
\begin{alignat}{1}
		\textcolor{blue}{E_{i}^{\text{I}}(t) =  \sum_{j \in \mathcal{J}}y_{i,j}(t) D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, }
	\label{16}
\end{alignat}
where $p_i^{\text{I}}$ is the standby energy consumption of MD $i \in \mathcal{I}$.  \textcolor{blue}{Recall that $y_{i,j}(t)$ is the offloading indicate function. Moreover, among all $j \in \mathcal{J}$, $y_{i,j}=1$ only for one $j$ which is the corresponding EN.}

%\textcolor{blue}{We also denote the total energy consumption for the offloaded task $z_{i,j}^{\text{E}}(t)$ in time slot $t$ as $E^{\text{O}}_i(t)$, which is,}
%\begin{alignat}{1}
%	\textcolor{blue}{E_i^{\text{O}}(t) = E_i^{\text{T}}(t) +  \textcolor{blue}{\sum_{\mathcal{J}}y_{i,j}(t) \,} E_{i,j}^{\text{E}}(t) + E_i^{\text{I}}(t)}.
%	\label{17}
%\end{alignat}

@@

\subsection{State Space}
A state in our MDP represents a conceptual space that comprehensively describes the state of an MD facing the environment. We represent the MD $i$'s state in time slot $t$ as vector $\boldsymbol{s}_i(t)$ that includes the newly arrived task size, the queues information, the MD's \textcolor{blue}{energy level of the battery}, and the workload history at the ENs. The MD observers this vector at the beginning of each time slot. The vector $\boldsymbol{s}_i(t)$ is defined as follows:
\begin{alignat}{1}
\boldsymbol{s}_i(t) = \Big(\lambda_i(t), \delta_i^{\text{C}}(t), \delta_i^{\text{T}}(t), \boldsymbol{\eta}_i^{\text{E}}\hspace{-0.4mm}(\hspace{-0.4mm}t\hspace{-0.4mm}-\hspace{-0.4mm}1\hspace{-0.5mm}),\phi_i(t), \mathcal{H}(t) \Big),
	\label{18}
\end{alignat}
where vector $\boldsymbol{\eta}_i^{\text{E}}(t-1) = (\eta_{i,j}^{\text{E}}(t-1))_{j \in \mathcal{J}}$ represents the queues length of MD $i$ in ENs at the previous time slot and is computed by the MD according to \eqref{10}. 
\textcolor{blue}{Since MDs are assumed to be battery-operated, their operation modes are aligned with those of real-world devices. Let $\phi_i(t)$ represent the \textcolor{blue}{battery level percentage of MD $i$} at time slot $t$, where $\phi_i(t)$ is selected from the discrete set $\Phi = \{\phi_1, \phi_2, \phi_3\}$, corresponding to ultra power-saving, power-saving, and performance modes, respectively.}

@@

\subsection{QoE Function}
\textcolor{blue}{The QoE function reflects user satisfaction with task computation, whether using local or edge resources. QoE accounts for task completion rate, processing delay, and energy consumption. Each user may have unique QoE requirements~\cite{wang2017qoe}. Therefore, we define a multi-dimensional, adaptive structure to assess QoE, balancing these factors according to the MDs preferences, such as prioritizing reduced task delays or energy savings, which may vary over time~\cite{wang2019intelligent},~\cite{mehrabi2019energy}. To capture personalized QoE requirements, we define QoE as a weighted sum of the above factors. Each MD dynamically adjusts these weights to reflect the importance of different factors based on its energy modes, which are performance, power-saving, and ultra-power-saving modes. We now calculate task delay and energy consumption and then introduce the associated cost and QoE function.}

@@

\textcolor{blue}{$\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+x_i(t) \bigg( E_i^{\text{T}}(t) + $
\begin{alignat}{1}
	\hspace{1.2cm}    E_i^{\text{I}}(t) +  \sum\limits_{j \in \mathcal{J}}  \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big)
	  E_{i,j}^{\text{E}}(t')\bigg).
	\label{22}  
\end{alignat}}
